%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[utf8]{inputenc}
\usepackage[english,italian]{babel}
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Matteo Dusefante} % Your name
\address{Rued Langgaards Vej 7, DK-2300 Copenhagen S, Denmark} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
%\address{(000)~$\cdot$~111~$\cdot$~1111 \\ madu@itu.dk} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	PERSONAL
%----------------------------------------------------------------------------------------

%\vspace{2cm}

\begin{rSection}{Personal}

\begin{tabular}{rl}
Name: & Matteo \\
Surname: & Dusefante \\
Date of Birth: & December 03, 1987 \\
Citizenship: & Italian \\
Address: & Rued Langgaards Vej 7, DK-2300 Copenhagen S, Denmark, Office 4B10 \\
%Phone: & +45 81 18 26 10 \\
Email: & \href{mailto:madu@itu.dk}{madu@itu.dk}
\end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Interests}

{\bf Algorithms and Data Structures } \\
Algorithms in External Memory and Parallel External Memory, Numerical and randomized algorithms.\\


\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf IT University of Copenhagen, Copenhagen} \hfill {\em September 2015 - Expected August 2018} \\ 
PhD Student in Computer Science \\
Member of the Algorithms research group, Computer Science Department. Research in algorithms on External Memory and Parallel External Memory.\\

{\bf University of Udine, Udine} \hfill {\em October 2010 - October 2014}\\ 
M.Sc. in Computer Science \\
Curriculum in languages and algorithms with specialisation in randomised and parallel algorithms, numerical algorithms, high performance computing, logic and object-oriented programming. Thesis on protein structure prediction protocols.\\

{\bf University of Udine, Udine} \hfill {\em October 2006 - October 2010}\\ 
B.Sc. in Computer Science \\
Curriculum focused on algorithms, formal methods, logic and object-oriented programming. Thesis on complexity analysis of multi agent systems.\\


\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND MENTIONS
%----------------------------------------------------------------------------------------

\pagebreak

\begin{rSection}{Research Activities}


{\bf Publications}

Matteo Dusefante and Riko Jacob,\\
\emph{An Empirical Evaluation of Permuting in Parallel External Memory},\\
Submitted, 2018.

Matteo Dusefante and Riko Jacob,\\
\emph{Cache Oblivious Sparse Matrix Multiplication},\\ 
To appear, LATIN, Latin American Theoretical Informatics, 2018.

Matteo Dusefante,\\
\emph{Las Vegas Boolean Matrix Multiplcication},\\ 
Manuscript, 2018.

{\bf Activities}

\emph{Swedish Summer School in Computer Science 2016, Stockholm}, June 2016,\\
\ind Hashing and Algorithms for Modern Parallel Systems.

\emph{Recent Advances in Algorithms Summer School, Saint Petersburg}, May 2017,\\
\ind Streaming Algorithms, Graph Algorithms and Continuous Optimization, Algorithms for \\ \ind High-Dimensional Data, Parameterized Algorithms.

\emph{Swedish Summer School in Computer Science 2017}, Stockholm, July 2017,\\
\ind Boolean Circuit Complexity, Algorithms and Lower Bounds.
%\end{addmargin}

\emph{Cache Oblivious Sparse Matrix Multiplication}, \\
\ind ARCO Workshop, IT University of Copenhagen, November 2017.
 

{\bf Collaborations}

Federico Campeotto, Alessandro Dal Palù, Agostino Dovier, Ferdinando Fioretto and Enrico Pontelli,\\
\emph{Experimenting with FIASCO for protein structure prediction},\\
In 10th Workshop on Constraint-Based Methods for Bioinformatics, Lyon, France, 2014.


\end{rSection}


%----------------------------------------------------------------------------------------
%	WORKING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Working Experiences}

{\bf IT University of Copenhagen} \hfill {\em September 2015 - Expected August 2018} \\ 
{ PhD Student} \hfill {\em Copenhagen, Denmark}

{\bf OverIT - Engineering Group} \hfill {\em April 2015 - August 2015} \\ 
{ Research and Development - Analyst} \hfill {\em Udine, Italy} \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Italian & Native Speaker \\
English & Full professional proficiency, C1 CEFR, IELTS overall score 7.0, Dec 2014 – Dec 2016 \\
German & Limited proficiency \\
%Danish & Beginner
\end{tabular}\\

\end{rSection}


%----------------------------------------------------------------------------------------
%	SKILLS AND COMPETENCES
%----------------------------------------------------------------------------------------

\newcommand{\CC}{C\nolinebreak\hspace{-.05em}\raisebox{.4ex}{\tiny\bf +}\nolinebreak\hspace{-.10em}\raisebox{.4ex}{\tiny\bf +}}

\begin{rSection}{Skills and Competences}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l } 
Software & \CC/C, Java, Python \\
& Prolog, Haskell, Curry, Constraint Logic Programming, Answer Set Programming \\
& Matlab, MPI
\end{tabular}

\end{rSection}

\end{document}
